\Large \bf 3-Step, 1-Factor Authentication With Custom-Fit, In-Ear EEG

### 2017-02-06 paper.tex
Set up to integrate figures for results
Added figures

\subsection{{\bfseries\sffamily TODO} Simulating an imposter attack}
\label{sec:orgdd6e8bd}
\section{Results}
\label{sec:org6705b1d}
\subsection{{\bfseries\sffamily TODO} Combinations of electrodes}
\label{sec:org21b14ae}

@@

@@

\underline{Table: FAR/FRR Between-subjects results by participant (avg. all tasks? Best task?)}

\underline{Our attempt to substantiate that we have both inherence and knowledge factors:}

\underline{Table: original strategy, within-subjects, within-tasks strategy; where each of those headings is subdivided into mean FAR, mean FRR (across all subjects and tasks)}

>>>>

\section{Results}
\label{sec:org6705b1d}
\subsection{{\bfseries\sffamily TODO} Combinations of electrodes}
\label{sec:org21b14ae}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./figures/mean-far-by-electrode-config.png}
\caption{FAR and FRR by electrode configuration. All electrodes combined achieves a perfect score. We achieve the next best scores using data from the left ear only.}
\end{figure}

% Include FRR here? (downisdes: FRR is way bigger, can't see FAR). Include LinearSVC here? (downsides: SVC FAR is way bigger, can't see FAR)

@@

\begin{table}[h]
\begin{center}
\begin{tabular}{rrrl}
FAR & FRR & subject & task\\
\hline
0.0 & 0.0 & 1 & listennoise\\
0.0 & 0.0 & 2 & breathe\\
0.0 & 0.0 & 3 & breathe\\
0.0 & 0.0 & 4 & breathe\\
0.0 & 0.012 & 5 & breathe\\
0.0 & 0.0 & 6 & breathe\\
0.0 & 0.0 & 7 & breathe\\
\end{tabular}
\end{center}
\caption{Best-case passthought FAR and FRR results by participant using data from the left ear.}
\end{table}

\underline{Our attempt to substantiate that we have both inherence and knowledge factors...}

\begin{table}[h]
\begin{center}
\begin{tabular}{lrrr}
 & Original & Within-tasks & Within-subjects\\
\hline
FAR & 0.000074 & 0.000724 & 0.00252\\
FRR & 0.00442 & 0.001522 & 0.0397\\
\end{tabular}
\end{center}
\caption{Mean FAR and FRR for all subjects and pssthoughts across three different training strategies.}
\end{table}

\underline{compared to within-tasks training, this original strategy gives us a higher FRR, but an FAR that's an order of magnitude lower. Put takeaways more clearly in the caption.}

% 1. Within-tasks performance
% 
% number of tasks with # far < 0.0001 AND frr < 0.01?
%            
% subject                                
% 001        5
% 002        6
% 003        6
% 004        9
% 005        6
% 006        9
% 007        4
% 
% 2. Within-subjects performance

% number of tasks with # far < 0.0001 AND frr < 0.01?
% 
% subject                                
% 001        1
% 002        1
% 003        6
% 004        3
% 005        1
% 006        3
% 007        5
%
% 3. Original for comparison
%
% here is the original training (right-subject, right-task vs. wrong-subject, any-task) FAR/FRR:
% 
% FAR  0.000074	
% FRR  0.004420
%
